

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}
\usepackage{textcomp}

\usepackage{xcolor}



\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Ahmed Skali}


% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = {blue!50!black},
  pdfauthor = {\name},
  pdfkeywords = {economics, political economy, development},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}


% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}



\vspace{0.25in}


\begin{tabular}{ll}





{\huge \name} \hspace{18ex}

& \\
& \\

\begin{minipage}{0.62\linewidth}
\begin{tabular}{lr}
c/o GEM Secretariat & \\
Faculty of Economics and Business & \\ 
University of Groningen & \\
  Nettelbosje 2, 9747 AE Groningen & \\
 The Netherlands & \\
\end{tabular}
\end{minipage}

&

\begin{minipage}{0.2\linewidth}
  \begin{tabular}{llllllllllllr}
  Email: & \href{mailto:a.skali@rug.nl}{a.skali@rug.nl} &&&&&&&&&&&  \\
   Homepage: & \href{ahmedskali.com}{ahmedskali.com}  &&&&&  &&&&&& \\
    Citizenship: & Australia, Morocco &&&&&  &&&&&& \\
  \end{tabular}
\end{minipage}
\end{tabular}


\section*{ Research Interests}

\begin{itemize}

\item Political economics, culture and institutions, human behaviour, economic development

\end{itemize}

\section*{ Current Roles}

\begin{itemize}
	
	\item Assistant Professor, Department of Global Economics \& Management, University of Groningen, 2021-
	\begin{itemize}
	\item Research Affiliate, \textit{Groningen Growth and Development Centre}, 2021-
	\item Research Affiliate, \textit{In the LEAD} Centre of Expertise, 2021-
	\item FEBRI Fellow, 2021-
	\end{itemize}
	\item Associate Editor \& Methods Advisor, \textit{The Leadership Quarterly}, 2024 -
	\item Editorial Board member, \textit{The Leadership Quarterly}, 2020 -
	\item Research Fellow, Centre for Behavioural Economics, Society and Technology, Queensland University of Technology, 2019 -
	\item Fellow, Global Labor Organization, 2023 -
	\item Affiliate, Households in Conflict Network (HiCN), 2023 -
\end{itemize}

		
\section*{Journal Articles}



\begin{itemize}

\item \textbf{Not all about the Money: Service Quality Information Improves Consumer Decision-Making}, with J Blijlevens, SH Chuah, A Neelim, and J Prasch
			\vspace{-0.05in}
\item \textit{Journal of Economic Behavior \& Organization}, forthcoming \href{https://ahmedskali.com/papers/ServiceQuality.pdf}{[Paper]}


\medskip

			\item {\bf Patience Predicts Attitudes towards Vaccination and Uptake of Vaccines}, with HF Chan, S Rizio and B Torgler
 			\vspace{-0.05in}
	\item \textit{Social Psychological and Personality Science}, 15 (2024) \href{https://journals.sagepub.com/doi/full/10.1177/19485506231189905/}{[Paper]}

\medskip
	
			\item \textbf{Child Labour and Psychosocial Well-Being: Findings from India}, with S Feeny, A Jyotishi, S Nath, A Posso and PK Viswanathan. 

	\vspace{-0.05in}
	
		\item \textit{Health Economics}, 30 (2021): 876-902. \href{https://drive.google.com/file/d/1I9yWtV-pGuyV0i0fq94jGkzt6pMkHtGl/view?usp=sharing}{[Paper]}
	
	\medskip
	
			\item {\bf Trust in Government in Times of Crisis:
		A Quasi-Experiment during the Two World Wars}, with  D Stadelmann and B Torgler. 
	
	\vspace{-0.05in}

		\item \textit{Journal of Comparative Economics}, 49 (2021): 277-289.  \href{http://www.crema-research.ch/papers/2019-04.pdf}{[Paper]} 

\medskip

	\item \textbf{Early COVID-19 Government Communication is Associated with Reduced Interest in the QAnon Conspiracy Theory}, with HF Chan, S Rizio and B Torgler.
		\vspace{-0.05in}

		\item \textit{Frontiers in Psychology}, 12 (2021): 681975. \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2021.681975/full}{[Paper]}

\medskip
	
		\item \textbf{Can Psychological Traits Explain Mobility Behavior During the COVID-19 Pandemic?} with HF Chan, J Moon, D Savage, B Torgler, and S Whyte. 
	\vspace{-0.05in}
		\item \textit{Social Psychological and Personality Science}, 12 (2021): 1018-1029.  \href{https://psyarxiv.com/5q3jv/}{[Paper]}

\medskip

\item			\textbf{The Additionality of R\&D Tax Policy: Quasi-Experimental Evidence}, with J Holt and R Thomson.  
\vspace{-0.05in}
\item \textit{Technovation}, 107 (2021): 102293. \href{https://doi.org/10.1016/j.technovation.2021.102293}{[Paper]}			 
\begin{itemize}
	\item Media: \href{ https://www.austaxpolicy.com/the-additionality-of-rd-tax-policy-evidence-from-australia/}{[AusTaxPolicy]} \href{https://theconversation.com/randd-tax-incentives-need-to-be-simple-and-underpin-investor-confidence-66273}{[The Conversation]} \href{https://www.industry.gov.au/sites/g/files/net3906/f/May\%202018/document/extra/research-and-development-tax-incentive-review-report-cie_0.pdf}{[Department of Industry]} \href{https://dataportal.arc.gov.au/EI/API/impact-studies/681/pdf}{[Australian Research Council]} \href{http://www.aamc.org.au/rd-study-incentives-double-our-money/}{[Australian Advanced Manufacturing Council]}
\end{itemize}


\medskip
	
	\item \textbf{How Confidence in Healthcare Systems Affects Mobility and Compliance during the COVID-19 Pandemic}, with HF Chan, M Brumpton, A Macintyre, J Arapoc, D Savage, D Stadelmann \& B Torgler. 
	
	\vspace{-0.05in}
	
	
	\item \textit{PLOS One} 15 (2020): e0240644.  \href{https://psyarxiv.com/86qxu/}{[Paper]}
	
\medskip	
	
	\item \textbf{How Does Globalization Affect COVID-19 Responses?}, with S Bickley, HF Chan, D Stadelmann, and B Torgler 

\vspace{-0.05in}

\item \textit{Globalization and  Health}, 17 (2021): 57. \href{https://globalizationandhealth.biomedcentral.com/articles/10.1186/s12992-021-00677-5}{[Paper]}


	\medskip
	
	\item \textbf{Masculinity Cues, Perceptions of Politician Attributes, and Political Behaviour}, with HF Chan, D Stadelmann, B Torgler, and S Whyte. 
	
	\vspace{-0.05in}

		\item \textit{Economics \& Politics} 33 (2021): 148-171. \href{xhttps://drive.google.com/file/d/1bwZzZJuU1phzjWLgCkL2H-tYz_4uJnxC/view?usp=sharing}{[Paper]}


		\medskip
		
		\item {\bf Risk Attitudes and Human Mobility During the
	COVID-19 Pandemic}, with HF Chan, D Savage, D Stadelmann, and B Torgler
	\vspace{-0.05in}

\item \textit{Scientific Reports}, 10 (2020): 19931 
\href{http://www.crema-research.ch/papers/2020-06.pdf}{[Paper]}

	\medskip
		
	\item \textbf{How Often Do Dictators Have Positive Economic Effects? Global Evidence, 1858-2010.} with S Rizio.
	 \textit{The Leadership Quarterly} 31 (2020): 101302. \href{https://drive.google.com/file/d/1gSZX3oPnJ9YWZwG0Px_6KRd62K9ZNPrj/view}{[Paper]}
	 	
	 \begin{itemize}
	 	\item 2020 Winner, \textit{The Leadership Quarterly} Best Paper Award
	 		\item Selected media: \href{https://www.independent.co.uk/news/business/news/strongman-leaders-economy-study-trump-dictators-a9018926.html}{[The Independent]}
	 		\href{https://qz.com/1688397/data-proves-it-authoritarian-leaders-are-bad-for-the-economy/}{[Quartz]} \href{https://www.abc.net.au/radionational/programs/drive/strongman-dictators-not-the-best-for-economy/11339196}{[ABC Radio]} 
	 		\href{https://www.theguardian.com/australia-news/live/2019/jul/23/national-security-labor-coalition-politics-live?page=with:block-5d3669f98f0845f89e312616#block-5d3669f98f0845f89e312616}{[The Guardian]}
	 		\href{http://theindependent.sg/strongman-leaders-make-for-weak-economies-study-finds/}{[The Independent Singapore]} \href{https://phys.org/news/2019-07-strongman-leaders-weak-economies.html}{[Phys.org]} \href{https://www.reduno.com.bo/nota/segun-estudios-dictadores-hacen-economias-debiles--2019723154528}{[Red Uno Bolivia]} \href{https://www.eurekalert.org/pub_releases/2019-07/ru-slm072219.php}{[Eurekalert]} \href{https://g7.hu/vilag/20190726/ritkan-viragzik-a-gazdasag-eroskezu-vezeto-uralma-alatt/}{[G7 Hungary]}
	 		\href{https://www.leistungstraeger.at/wcms/leistung/news.asp?nnr=74375}{[Leistungstraeger Austria]}
	 		\href{https://www.pressetext.com/news/starke-fuehrer-bedeuten-schwache-wirtschaft.html}{[Pressetext Switzerland]} \href{http://nauka.offnews.bg/news/Novini_1/Silnite-lideri-vodiat-do-slabi-ikonomiki_133949.html?allr=&order=DESC}{[OFFNews Bulgaria]} \href{https://democracychronicles.org/strongman-leaders-make-for-weak-economies-study-finds/}{[Democracy Chronicles]} \href{https://www.scimex.org/newsfeed/strongman-leaders-make-for-weak-economies,-study-finds}{[Scimex]}
	 		\href{https://marginalrevolution.com/marginalrevolution/2019/07/friday-assorted-links-219.html?utm\_source=feedburner\&utm\_medium=feed\&utm\_campaign=Feed\%3A+marginalrevolution\%2Ffeed+\%28Marginal+Revolution\%29}{[Marginal Revolution]}
	 \end{itemize}
	 
	\medskip
			
	\item {\bf The Ethics of Student Participation in Economic Research: Arguments and Evidence}, with R Hoffmann, J Blijlevens, SH Chuah, A Neelim, and J Laban 
	\vspace{-0.05in}
	\item \textit{Journal of Behavioral and Experimental Economics} 85 (2020), 101521. \href{https://drive.google.com/file/d/1Y8XeVvO7n-5MLq2QLrcQBe_YFtjxAEll/view?usp=sharing}{[Paper]} 
		
	
	\medskip
	
				  \item \begin{flushleft} {\bf Moralizing Gods and Armed Conflict}. \linebreak \textit{Journal of Economic Psychology} 63 (2017), 184-198. \href{https://drive.google.com/file/d/0BwqbQjw0aU48bWlWVkEwRC1Ma0E/view?usp=sharing}{[Paper]} 
				  \end{flushleft}			  
				  	\vspace{-0.05in}
				  \begin{itemize}
				  	Media: \href{https://www.nationalaffairs.com/blog/detail/findings-a-daily-roundup/blessed-and-cursed}{[National Affairs]}
				  \end{itemize}
				  
	
	\medskip
	
\item {\bf Does Democracy Drive Income in the World, 1500-2000}, with JB Madsen and PA Raschky. \linebreak {\textit{European Economic Review}} 78 (2015), 175-195. \href{http://www.sciencedirect.com/science/article/pii/S0014292115000707}{[Paper]} 
				  
\vspace{-0.05in}
\begin{itemize}
	Media: \href{https://voxeu.org/article/revisiting-causal-effect-democracy-long-run-development}{[VoxEU]} \href{https://blogs.elespectador.com/economia/el-mal-economista/y-la-democracia-para-que}{[El Espectador]} \href{https://www.nationalaffairs.com/blog/detail/findings-a-daily-roundup/backward}{[National Affairs]}
\end{itemize}

\end{itemize}

\section*{Many-Lab Articles}

		\begin{itemize}
	\item \textbf{Social and moral psychology of COVID-19 across 69 countries}, with F Azevedo et al. 
			\vspace{-0.05in}
	\item \textit{Scientific Data}, 10 (2023), 272.  \href{https://psyarxiv.com/a3562/}{[Paper]}
\end{itemize}

\medskip


\begin{itemize}
	\item \textbf{Predicting Attitudinal and Behavioral Responses to the COVID-19 Pandemic using Machine Learning}, with T Pavlovic et al. 
		\vspace{-0.05in}
\item \textit{PNAS Nexus}, 1(3) (2022), pgac093.   \href{https://doi.org/10.1093/pnasnexus/pgac093}{[Paper]}
\end{itemize}


		\medskip


\begin{itemize}
	\item \textbf{National Identity Predicts Public Health Support during a Global Pandemic}, with J Van Bavel et al. 
		\vspace{-0.05in}
\item \textit{Nature Communications}, 13 (2022): 517. \href{https://www.nature.com/articles/s41467-021-27668-9}{[Paper]}
\end{itemize}


\section*{Book Chapters}

\begin{itemize}

	\item {\bf Perverse Social Norms}, with B. Torgler and E. Yoeli (2024, forthcoming). In: S.H. Chuah, R. Hoffmann and A. Neelim (eds.), \textit{Edward Elgar Encyclopedia of Behavioural and Experimental Economics}. Cheltenham, UK: Edward Elgar. \href{https://drive.google.com/file/d/132rMWFxxwCWb974hB2EOs1SABoPdYFEX/view}{[Paper]}
		
	\medskip

	\item {\bf Behavioural Cliometrics}, with B. Torgler (2024, forthcoming). In: S.H. Chuah, R. Hoffmann and A. Neelim (eds.), \textit{Edward Elgar Encyclopedia of Behavioural and Experimental Economics}. Cheltenham, UK: Edward Elgar. \href{https://drive.google.com/file/d/132rMWFxxwCWb974hB2EOs1SABoPdYFEX/view}{[Paper]}
	
	\medskip

	\item {\bf The Detective Mindset: Forensic Approaches to Detecting Behaviour} (2021). In: J. Blijlevens, M. Elkins, and A. Neelim (eds.), \textit{Behavioural Business: The Psychology of Decisions in Economy, Business and Policy Contexts}. Singapore: Springer Nature. \href{https://drive.google.com/file/d/132rMWFxxwCWb974hB2EOs1SABoPdYFEX/view}{[Paper]}
	
	\medskip
	
	\item {\bf Foreign Aid and Development Goals: Revisiting the Evidence}, with E Munyanyi and S Awaworyi Churchill (2020). In: S Awaworyi Churchill (ed.), \textit{Moving from the Millennium to the Sustainable Development Goals: Lessons and Recommendations}. London: Palgrave MacMillan. \href{https://link.springer.com/chapter/10.1007\%2F978-981-15-1556-9_9}{[Paper]}
	



\end{itemize}


\section*{Working Papers}
				
				\begin{itemize}
				
						\item \textbf{Wealth Inequality and Economic Growth: Evidence from the World Inequality Database}, with R. Steenbrink.  \href{https://www.econstor.eu/handle/10419/289584}{[Paper]}
 
						\begin{itemize}
							\item \textit{R\&R World Development}
							\end{itemize}
	

	
		\medskip
	
		\item {\bf The Cost of Nativism: Evidence from the Netherlands}, with H. Garretsen. 
 \href{https://ahmedskali.com/papers/LanguagePaper.pdf}{[Paper]}
	
	\medskip
	
		\item \textbf{Violent Conflict and Parochial Trust: Survey and Lab-in-the-Field Evidence}, with K. Werner. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4294035}{[Paper]}
	
\medskip
	
	\item {\bf Political Entrenchment and GDP Misreporting}, with H.F. Chan, B. Frey and B. Torgler. 
 \href{https://www.cesifo.org/DocDL/cesifo1_wp7653.pdf}{[Paper]}
	

		\medskip


		\item \textbf{Transportation Infrastructure and Child Mortality: Sub-National Evidence for 22 Developing Countries}, with R. Boot.  \href{https://ahmedskali.com/papers/TransportationCM.pdf}{[Paper]}
								
				\medskip	

	\item \textbf{How Large is the Beauty Premium in Politics?}, with S. Bickley, H.F. Chan, D. Stadelmann, B. Torgler, and S. Whyte.  \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4273311}{[Paper]}
 
				\medskip

	

\item \textbf{A Global Dataset of Human Mobility}, with HF Chan and B Torgler. \href{https://drive.google.com/file/d/1\_0UwLGb5UwmHztSybZu\_1er8125UCmy0/view}{[Paper]}	


 
\end{itemize}


\section*{Education}

\begin{itemize}
	\item Ph.D., Department of Economics, Monash University, October 2015
	\subitem Thesis title: {\emph{Essays in Political Economy}}
	\item M.A., Economics, University of Delaware, 2008 
	\item M.A., Monnaie, Finance et Gouvernance, Universit\'e Lumi\`ere Lyon 2, 2008
	\item B.S., Economics, University of Delaware, 2006
	\item Licence en Sciences Economiques et de Gestion, Universit\'e Lumi\`ere Lyon 2, 2005
	\item Visiting student, Universitat de Barcelona, 2004-05
\end{itemize}

\section*{ Previous Roles}

\begin{itemize}
	
	\item Alfred Deakin Research Fellow, Department of Economics, Deakin University, 2020
	
	\item Lecturer, Department of Economics, Royal Melbourne Institute of Technology, 2017 - 2020
	
	\item Research Affiliate, QuBE, Queensland University of Technology, 2016 - 2019
	
	\item Research Fellow, Faculty of Business and Law, Swinburne University of Technology, 2015 - 2016
	
\end{itemize}




\section*{Professional Activity}
\begin{itemize}
	
		\item Professional roles:
	\begin{itemize}
			\item Editorial Board member, \textit{The Leadership Quarterly}, 2020 -
			\item Steering committee member, Centre for Public Health in Economics and Business, University of Groningen, 2022 -
		\item Chair, Economics of Religion Research Cluster, RMIT, 2017 - 2018
		\item  Deputy Chair, Behavioural Business Lab, RMIT, 2018 - 2020
		\item Advisor, Business College Human Ethics Advisory Network, RMIT, 2018 - 2020
		\item Economics Seminar Coordinator, Swinburne University of Technoloy, 2016
	\end{itemize}


	\item Conference and seminar presentations (including scheduled):
	\begin{itemize}
		\item \textit{2024}: Culture and Institutions Workshop (Radboud University Nijmegen). \textit{2023}: Hamburg Lectures in Law and Economics, ASREC, Households in Conflict Network (HiCN) workshop (ULB Brussels), European Public Choice Society. \textit{2022:}  Cultures of Trust and Institutions of Freedom Workshop (IFN Stockholm), University of Groningen. \textit{2021:} KVS New Papers Workshop. \textit{2020:} University of Tokyo, University of Groningen, Università di Padova. \textit{2019:} Harvard University, MIT Sloan, University of California - Irvine, ASREC (Association for the Study of Religion, Economy and Culture) Conference, Monash University, Australian Conference of Economists, Australasian Public Choice Conference, Deakin University Annual Workshop on Natural Experiments in History.  \textit{2018:} Pacific Trade and Development (PAFTAD) Conference (Japan Center for Economic Research), RMIT. \textit{2017}: European Winter Meeting of the Econometric Society (Barcelona GSE), The University of Melbourne School of Psychological Sciences, Society for the Advancement of Behavioural Economics (SABE) Conference (University of Newcastle), RMIT, Australasian Public Choice Conference (Deakin University). \textit{2016:} Public Choice Society Meetings (Fort Lauderdale, FL), University of Melbourne, Economics and Biology of Contests Conference (Queensland University of Technology), Monash University, RMIT. \textit{Pre-2016: }Australasian Public Choice Conference (Queensland University of Technology), Asia-Pacific Innovation Conference (Zhejiang University), Australasian Development Economics Workshop (Monash University), Swinburne University of Technology, University of St. Gallen, Monash University, 2014 Monash Centre for Development Economics and Sustainability Workshop, 2014 Australasian Public Choice Conference (Monash University), RMIT
	\end{itemize}
	
	\item Academic visits:
	
	\begin{itemize}
				\item Centre for Behavioural Economics, Society and Technology, Queensland University of Technology, December 2019
		\item Chair of Development Economics, University of Bayreuth, January 2018
		\item School of Economics and Finance, Queensland University of Technology, October 2016 - December 2016
	\end{itemize}
	
	\item Conference organization:
	\begin{itemize}
		\item	2020 Natural Experiments in History Workshop, 2018 Australasian Public Choice Conference
	\end{itemize}
	

	
	\item Refereeing:
	\begin{itemize}
		
		\item The Leadership Quarterly, Health Economics, Journal of Economic Behavior \& Organization, Journal of Population Economics, Economic Inquiry, Journal of Economics \& Management Strategy, Regional Studies, Cambridge Journal of Regions, Economy, and Society; Scientific Reports, Kyklos, Technovation, Empirica, Economics Bulletin, Review of World Economics {\textit{(Welt-wirtschaftliches Archiv)}}, Humanities and Social Sciences Communications, Economic Modelling, Science and Public Policy	\end{itemize}
	
	\item Conference discussant:
	\begin{itemize}
		
		\item 2023 European Public Choice Society, 2018 Pacific Trade and Development Conference, 2016 Public Choice Society Meetings
	\end{itemize}
	
	\item PhD supervisions:
	\begin{itemize}
		\item Ongoing: Sam Oxley, Sophie von Rußdorf
	\end{itemize}
	
		\item Master's supervisions:
	\begin{itemize}
		\item MSc Economic Development \& Globalization: 7 completed theses, 2021 - date
	\end{itemize}
	
	\item Thesis examinations:
	\begin{itemize}
		\item PhD: Monash University (2018), University of Newcastle (2022), Deakin University (2024)
		\item Honours: Queensland University of Technology (2017, 2018)
	\end{itemize}
	
	
\end{itemize}



\section*{Awards and Competitive Funding}
\begin{itemize}
	\item Top 5 best teacher, Faculty of Economics and Business, University of Groningen, Spring 2021
	\item Co-Investigator: Behavioural Insights for Societal and Business Impact. RMIT, 2019, \$4,550
	\item Co-Investigator: Service Quality and Consumer Choice in the Victoria Energy Retail Market. Consumer Policy Research Centre, 2018, \$73,853
	\item Early Career Researcher Publication Award. RMIT, 2018, \$4,980
	\item PAFTAD Young Fellow, 2018
	\item Co-Investigator: Seed Funding, International Development and Trade Research Group. RMIT, 2017, \$38,000
	\item Dean\textquotesingle s Postgraduate Research Excellence Award. Monash University, 
	2010-13 	
	\item Monash Postgraduate International Research Scholarship. Monash University, 2010-14 	
	\item Monash Graduate Scholarship. Monash University, 2010-14
	\item Graduate Research Award (best master's thesis), Department of Economics, University of Delaware, 2008
	\item Explo\textquotesingle ra Scholarship. Rh\^one-Alpes Region, 2004-05, 2007-08
	\item Omicron Delta Epsilon, 2006
	
\end{itemize}












\section*{Teaching}
\begin{itemize}
	
	\item \textit{University of Groningen}: EBB811B05 Growth and Development Economics, EBP810B05 International Economics, EBM206A05 Globalization Debates, EBB142A05 Sustainability and Globalization
	
	\smallskip
	
	\item \textit{Royal Melbourne Institute of Technology}: ECON1020 Prices and Markets, ECON1238 Econometric Techniques, ECON1339 Behavioural Business
	
	
	
	\smallskip
	
	
	
	\item \textit{Monash University}:  ECF2731 Managerial Economics, ECC3810 Public Finance, ECF3121 Economics of International Trade, ECF3120 Consumer Economics
	
	\smallskip
	\item \textit{Australian Catholic University}: ECON102 Microeconomics I
	
		\smallskip
	\item \textit{Guest lectures:} Climate change: an overview (Erasmus University Rotterdam, 2022); The perils of leadership without constraints (Royal Melbourne Institute of Technology, 2018, 2019).
	
	
\end{itemize}



\section*{References}

\begin{tabular}{lr}
	% Referee 1
	\begin{minipage}[t]{3.4in}
		Professor Christian Bjørnskov \\
		Department of Economics \& Business Economics \\
		Aarhus University\\
		Denmark \\
		\href{mailto:chbj@econ.au.dk}{chbj\textrm{@}econ.au.dk}
	\end{minipage}
	&
	% Referee 2
	\begin{minipage}[t]{3.4in}
		Professor Jakob B. Madsen\\
		Department of Economics\\
		The University of Western Australia\\
		Perth, Australia \\
		\href{mailto:jakob.madsen@uwa.edu.au}{jakob.madsen\textrm{@}uwa.edu.au}
	\end{minipage}
	\\
	\\
\end{tabular}

\begin{tabular}{lr}
	% Referee 1
	\begin{minipage}[t]{3.4in}
		Professor Paul A. Raschky \\
		Department of Economics \\
		Monash University \\
		Melbourne, Australia \\
		\href{mailto:paul.raschky@monash.edu}{paul.raschky\textrm{@}monash.edu}
	\end{minipage}
	&
	% Referee 2
		\begin{minipage}[t]{3.4in}
		Professor Benno Torgler \\
		School of Economics \& Finance \\
		Queensland University of Technology \\
		Brisbane, Australia \\
		\href{mailto:benno.torgler@qut.edu.au}{benno.torgler\textrm{@}qut.edu.au}
	\end{minipage}
	\\
	\\
\end{tabular}




\bigskip

% Footer
%\begin{center}
  %\begin{footnotesize}
   % Last updated: \today \\
  %\end{footnotesize}
%\end{center}

\end{document}